Blocking-resistant communication\\through domain fronting

### 2015-02-11 docs/fronting.tex
Fix clients-lantern graphic.
Add Psiphon text.
Unedited except for cites and typographic conventions.

\begin{figure}
\centering
\includegraphics[height=1.5in]{lantern}
\caption{
Megabytes per second served by domain-fronted Lantern proxies
(Lantern-hosted and peers).
}
\label{fig:lantern-bandwidth}
\end{figure}

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.

Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with
Psiphon
The decrease at the end of June
was caused by an unblocking event that made \meek unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

how clients choose a technique

unfronted mode

users: Figure~\ref{fig:clients-psiphon3}

>>>>

\begin{figure}
\centering
\includegraphics[height=1.5in]{clients-lantern}
\caption{
Megabytes per second served by domain-fronted Lantern proxies
(Lantern-hosted and peers).
}
\label{fig:lantern-bandwidth}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with
Psiphon.
We don't have user accounts or track users by e.g., IP address. We do
count connection events. The unique user number is derived from a
coarse-grained ``last connected'' timestamp sent by clients: if the last day
connected is before day being counted, then that connected event is a
unique user for that day.
}
\label{fig:clients-psiphon3}
\end{figure}

The Psiphon circumvention system~\cite{psiphon} is a centrally managed, geographically
diverse network of thousands of proxy servers. Psiphon is a
performance-oriented, ``one hop'' proxy architecture. Much of our server
infrastructure is hosted with cloud providers. As of January 2015, Psiphon
has over 2 million daily unique users.

Psiphon deploys clients for popular platforms, including Windows and
Android. Our clients are designed to tunnel a broad range of host traffic:
web browsing, video streaming, and mobile app data transfer. Psiphon
clients are designed for ease of use, and users are not asked to perform
any manual configuration.

As a circumvention system, Psiphon has faced threats including blocking by
DPI---both blacklisting and whitelisting---and blocking by network
end-points. For example, in 2013, Psiphon circumvented DPI which
whitelisted HTTP by sending a ``HTTP prefix''---the first few bytes of an
HTTP request---before the start of its regular upstream flow~\cite{information-controls}.

Psiphon takes measures to distribute its server addresses in such a way
that most clients discover enough servers to have several options in the
case of a server being blocked, while making it difficult to enumerate all
servers. In February 2014, Psiphon was specifically targeted for blocking
by network end-point, and this blocking was sufficiently aggressive to have
major impact on our user base, though not all users were blocked. As part
of our response we integrated and deployed fronting with meek. We fully
deployed this in June 2014. Our implementation is largely based on Tor's
meek-client and meek-server, with some modifications.

Psiphon employs meek as two distinct protocols: fronted meek, and what we
call ``unfronted meek''. Fronted meek uses the domain fronting technique.

In unfronted meek, we omit the TLS layer and the protocol on the wire is
HTTP. As fully compliant HTTP, unfronted meek supersedes our HTTP prefix
defense against HTTP whitelisting. Unfronted meek is not routed through
CDNs, and as such is only a DPI whitelist defense and not a defense against
enumeration of our network end-points. We envision a potential fronted HTTP
protocol with both properties, which requires cooperating with CDNs to
route our HTTP requests based on, for example, some obfuscated HTTP header
element.

\subsection{Implementation}

Psiphon's core protocol is SSH. SSH provides an encryption layer for
communication between Psiphon clients and servers; the primary purpose of
this encryption is to frustrate DPI. On top of SSH, we add an obfuscation
layer~\cite{obfuscated-openssh} that transforms the SSH handshake into a random stream; and
random padding of packets in the SSH handshake sequence. Psiphon clients
authenticate servers using SSH public keys obtained through out-of-band
channels, a process that is bootstrapped with server keys embedded in the
client binaries.

Our obfuscated SSH is the payload for the meek transport. As such, the meek
payload appears to be random data and lacks a trivial packet size signature
in its initial requests and responses.

In Psiphon's modified meek protocol, the session ID cookie contains
additional payload: a protocol version number, and the destination Psiphon
server address. As this cookie will be plaintext in unfronted meek, the
payload is encrypted---with NaCl crypto\_box---using a public key
associated with the destination meek-server; then obfuscated; then
formatted as an innocuous-appearing cookie with a randomly selected key
value. The protocol version number is used by meek-server to determine if
the meek-client supports several enhancements we have added. The server
address is the destination SSH server that meek-server forwards traffic to.

We further modified the meek protocol so that the meek-clients only
transmits its chosen session ID on the first meek HTTP request, after which
the meek-server assigns a distinct ID to be used on subsequent requests.
This allows meek-server to distinguish between new and existing sessions
when a meek-client sends a request after a long delay, such as after an
Android device awakes from sleeping, where the meek-server may have already
expired and discarded its session.

Psiphon ported meek-client to Java for our Android client. For Android, we
make HTTP and HTTPS requests using the Apache HttpClient component, with
the expectation that this will have characteristics similar to TLS sessions
for other Android apps making web service requests.

The Psiphon meek-server inspects CDN injected headers to determine user
client IP address. The address is mapped to a region and the region is used
to record usage statistics.

\subsection{Server Selection}

When a user starts a Psiphon client, the client initiates connections to up
to 10 different servers simultaneously, keeping the first fully established
connection. Candidate servers are chosen at random from cached lists of
known servers and a mix of different protocols are used. The purpose of the
simultaneous connections are to minimize user wait time in case certain
protocols are blocked, certain servers are blocked by address, or certain
servers are at capacity and rejecting new connections. This process also
helps us with automatically using the lowest latency server for the user as
it tends to pick the closest data center, and lowest cost as it tends to
pick direct connections over fronted due to lower latency.

We made two modifications to server selection to accommodate fronting.
First, we changed the notion of an established connection from TCP
connection completion to full SSH handshake completion. This ensures the
full two hops are measured in the fronted case. Second, we adjusted our
protocol selection schedule to ensure that, while we generally favor the
fastest connection, we do not expose our system to an attack that forces us
to always use a degraded protocol. For example, the adversary could
implement a DPI attack that allows all connections to establish but then
terminate or severely throttle non-whitelisted protocols after some short
time period. If we detect such degraded conditions, we shift protocol
selection in favor of unfronted and fronted protocols over the faster
obfuscated SSH direct connections.

\subsection{Performance}

For clients, we identified a need to improve video streaming and download
performance for traffic tunneled through meek. In addressing this, our
considerations included a cost-per-HTTP-request for some candidate CDNs,
lack of support for HTTP pipelining in our components, and a concern about
the DPI signature of upstream-only or downstream-only HTTP connections. So,
as a compromise, we made a tweak to the meek protocol: instead of sending
at most 64K of payload in each HTTP response, response data will be
streamed back, using chunked encoding, as long as there is data to send and
for no longer than 200 milliseconds.

This tweak yielded a significant performance improvement, with download
speeds increasing by 4--5×, and 1080p video playback becoming smooth. Under
heavy downstream conditions, we observe peak payloads of 1MB, with 300k on
average, although the exact traffic signature is highly dependent on the
tunneled application. We tuned the timeout parameter through subjective
usability testing focusing on latency while web browsing and simultaneously
downloading large files.
